\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}

\pagestyle{empty}
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \large\bfseries
}{}{0em}{}[\titlerule]

\begin{document}

%----------HEADER----------
\begin{center}
    {\LARGE \textbf{Alex Carter}} \\[4pt]
    New York, USA \\ 
    +1 (555) 234-5678 \\
    \href{mailto:alexcarter@email.com}{alexcarter@email.com} $|$
    \href{https://linkedin.com/in/alexcarter}{linkedin.com/in/alexcarter}
\end{center}

%----------SUMMARY----------
\section*{Professional Summary}
Motivated business graduate with experience in project coordination, data analysis, and client relationship management. Skilled at collaborating with cross-functional teams and delivering solutions that improve operational efficiency.

%----------EDUCATION----------
\section*{Education}
\textbf{Bachelor of Business Administration} \hfill 2019 -- 2023 \\
University of California, Los Angeles (UCLA) \\
Relevant Coursework: Marketing Analytics, Financial Management, Entrepreneurship

%----------EXPERIENCE----------
\section*{Experience}

\textbf{Business Analyst Intern} \hfill June 2023 -- Aug 2023 \\
TechWave Solutions, San Francisco, CA
\begin{itemize}[leftmargin=*]
\item Assisted senior analysts in gathering and analyzing business requirements for enterprise software projects.
\item Created reports and dashboards to track key performance indicators and operational trends.
\item Coordinated with cross-functional teams to streamline communication and project updates.
\end{itemize}

\textbf{Sales Associate} \hfill May 2022 -- May 2023 \\
Bright Retail Group, Los Angeles, CA
\begin{itemize}[leftmargin=*]
\item Increased monthly sales by 15\% through proactive customer engagement and product recommendations.
\item Maintained inventory records and supported store operations.
\item Assisted in organizing promotional campaigns and marketing displays.
\end{itemize}

%----------PROJECTS----------
\section*{Projects}

\textbf{Market Research Analysis}
\begin{itemize}[leftmargin=*]
\item Conducted a comprehensive market analysis for a startup product launch.
\item Analyzed consumer trends and competitor strategies using Excel and data visualization tools.
\end{itemize}

\textbf{Customer Experience Improvement}
\begin{itemize}[leftmargin=*]
\item Designed a feedback system that helped improve customer satisfaction by identifying service gaps.
\end{itemize}

%----------SKILLS----------
\section*{Skills}
\begin{itemize}[leftmargin=*]
\item Data Analysis: Excel, Power BI, SQL
\item Business Tools: Microsoft Office, Google Workspace
\item Soft Skills: Communication, Problem Solving, Team Leadership
\end{itemize}

%----------CERTIFICATIONS----------
\section*{Certifications}
\begin{itemize}[leftmargin=*]
\item Google Data Analytics Certificate
\item Project Management Foundations
\end{itemize}

\end{document}